A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-03-22 analysis/paper/supp_notes/supp_note_trajectory_inference_methods.Rmd
update results

---
title: "A comparison of single-cell trajectory inference methods: towards more accurate and robust tools"
bibliography: ../references.bib
csl: ../nature-biotechnology.csl
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{tabu}
  - \usepackage[normalem]{ulem}
  - \usepackage{lscape}
  - \usepackage{pbox}
  - \usepackage[labelformat=empty]{caption}
  - \ExecuteBibliographyOptions{sorting=none,sortcites=true,autocite=superscript,autopunct=false}
mainfont: Open Sans
output: 
  pdf_document: 
    latex_engine: xelatex
    dev: png
    keep_tex: true
    citation_package: biblatex
---

>>>>

---
title: "A comparison of single-cell trajectory inference methods: towards more accurate and robust tools"
bibliography: ../references.bib
csl: ../nature-biotechnology.csl
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{tabu}
  - \usepackage[normalem]{ulem}
  - \usepackage{lscape}
  - \usepackage{pbox}
  - \usepackage[labelformat=empty]{caption}
  - \ExecuteBibliographyOptions{sorting=none,sortcites=true,autocite=superscript,autopunct=false}
mainfont: Open Sans
output: 
  pdf_document: 
    latex_engine: xelatex
    keep_tex: true
    citation_package: biblatex
---
